DisCon Kids Pilot

### 2019-01-16 analysis/02_kids.Rmd
update analysis file

files <- dir("../../kids_simple_4cat/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../kids_simple_4cat/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$data$data)
  raw_data <- bind_rows(raw_data, id)
}

>>>>

files <- dir("../../kids_simple_4cat/")
#files <- dir("../../kids_raw_data/600/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../kids_simple_4cat/",f,sep="")
#  jf <- paste("../../kids_raw_data/600/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$data$data)
  raw_data <- bind_rows(raw_data, id)
}
